Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-11-21 revise/revise.tex

\question The paper presents an interesting and original work on a new solver
for MSRs based on the MOOSE platform.  It is clearly written but it lacks depth
both in the description of the work and in the positioning of it in the
available scientific literature.  In addition, the paper fails in properly
supporting the main claim of an ``unmatched fidelity in coupled neutronics and
thermal hydraulics MSR simulation'', since the proposed results are limited and
compared only with an old MSRE model. The paper would represent an interesting
contribution to the scientific community but it requires revision. In
particular the authors should deepen their bibliographical research, and
include a comparison either with experimental results or with other
state-of-the-art tools.
\begin{solution}
        The statement concerning `unmatched' fidelity has been removed 
        entirely.
\end{solution}

@@

\question The proposed scaling test is very limited. Proper scaling tests would require weak and strong scaling tests, an assessment on the impact of the size of problem per core, a separate assessment of intra-node and extra-node scaling, etc. In addition, information should be provided on the employed numerical algorithms and on the parallelization strategy. The authors should either extend significantly the section, or remove it completely.
\begin{solution}
        <++>
\end{solution}

>>>>

\question The paper presents an interesting and original work on a new solver
for MSRs based on the MOOSE platform.  It is clearly written but it lacks depth
both in the description of the work and in the positioning of it in the
available scientific literature.  In addition, the paper fails in properly
supporting the main claim of an ``unmatched fidelity in coupled neutronics and
thermal hydraulics MSR simulation'', since the proposed results are limited and
compared only with an old MSRE model. The paper would represent an interesting
contribution to the scientific community but it requires revision. In
particular the authors should deepen their bibliographical research, and
include a comparison either with experimental results or with other
state-of-the-art tools.
\begin{solution}
        <++>
\end{solution}

@@

\question The proposed scaling test is very limited. Proper scaling tests would require weak and strong scaling tests, an assessment on the impact of the size of problem per core, a separate assessment of intra-node and extra-node scaling, etc. In addition, information should be provided on the employed numerical algorithms and on the parallelization strategy. The authors should either extend significantly the section, or remove it completely.
\begin{solution}
        We are performed strong and weak scaling up to 768 cores separately for intra-node and extra-node cases. Parallelization implemented using LibMesh library (for automatical domain decomposition) and PetSc library which contains set of parallel solvers. Detailed information added in Section 4.3 introduction.
\end{solution}
